Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-06 outputs/paper/presentation.qmd
Updates to paper.qmd
Updates to presentation

---
title: "Untitled"
format: pptx
editor: visual
---

@@

>>>>

---
#### Preamble ####
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
email: "sarah.mansoor@mail.utoronto.ca"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pptx
editor: visual
toc: true
# bibliography: references.bib
---

@@

![](images/paste-01E2A963.png)
